---
title: "Data_Vis"
author: "Team OK: Kara Wei, Ouyang Du"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(ggplot2)
library(dplyr)

```

```{r}
library(mice)
```

```{r}

# Specify the file path to your CSV file
file_path <- "/Users/karawei/Desktop/GRAD 3rd/ESE 527/garments_worker_productivity.csv"  # Replace with the actual path to your CSV file

# Use read.csv() to read the CSV file into a data frame
data_prod <- read.csv(file_path)
#replacing misplaced 'finishing ' with "finishing
data_prod$department = replace(data_prod$department, data_prod$department=="finishing ", "finishing")
head(data_prod)
nrow(data_prod)
```

We first draw out all the histograms for our numerical variables to see the distributions of them.

## Histograms of all numerical variables:

```{r}
par(mfrow = c(3, 4))
hist(data_prod[["actual_productivity"]],main="Productivity Index",xlab="Productivity Index")
hist(data_prod[["targeted_productivity"]],main="Target Productivity",xlab="Productivity Index")
hist(data_prod[["smv"]],main="Standard Minute Value",xlab="Minutes Needed for Task")
hist(data_prod[["over_time"]],main="Over Time",xlab="Minutes of Over Time")
hist(data_prod[["wip"]],main="Work in Progress",xlab="Number of Unfinished Products")
hist(data_prod[["incentive"]],main="Financial Incentive",xlab="Bangladash Taka(BDT)",breaks=200)
hist(data_prod[["idle_time"]],main="Idle Time",xlab="Amount of Time When Production was Interrupted")
hist(data_prod[["idle_men"]],main="Idle Workers",xlab="Number of Idle Workers When Production was Interrupted")
hist(data_prod[["no_of_style_change"]],main="Number of Style Change",xlab="Number of Style Change")
hist(data_prod[["no_of_workers"]],main="Number of Workers in a Team",xlab="Number of Workers in a Team")
```

We notice that wip has many missing (NA) values.  

We consider the following ways:

## 1) We try to make remove all rows with missing values.

```{r}
cleaned_data <- na.omit((data_prod))
head(cleaned_data)
nrow(cleaned_data)
```

As shown above, this costs a size reduction from 1197 rows to 691 rows.

## 2) Replace all NA values to 0s.

```{r}
data_replaced_by_zero <- data_prod
data_replaced_by_zero$wip <- replace(data_replaced_by_zero$wip,is.na(data_replaced_by_zero$wip),0)
head(data_replaced_by_zero)
```

Now our data set looks complete. The only concern is that given wip values seem to be far away from 0. Adding such 0 might cause outliers and biased data.

## 3) Calculate the mean with all zero values removed. Replacing the NA values w/ such mean.

```{r}
data_replaced_by_mean <- data_prod
data_replaced_by_mean$wip <- replace(data_replaced_by_mean$wip,is.na(data_replaced_by_mean$wip),mean(data_replaced_by_mean$wip,na.rm = TRUE))
head(data_replaced_by_mean)
cat("The mean of wip after removing all NA value rows is", mean(data_replaced_by_mean$wip,na.rm = TRUE))
```

```{r}
ggplot(data = data_prod, aes(x = wip)) +
  geom_histogram(binwidth = 1000) +
  scale_x_continuous(limits = c(0, 24000), breaks = seq(0, 24000, by = 2000))+
  scale_y_continuous(limits = c(0, 700))+
  labs(title = "Histogram of wip",
       x = "wip",
       y = "Frequency") + 
  theme_classic()
```

As we can see, most of the values are concentrated within the wip range from 0 to 2000. Our mean is 1190.466, which means our mean and mode are quite close. Our idea of replacing with mean makes sense. However, just to be more accurate, we preform the same idea with median replacement and make sure they are all consistent.

## 4) Replacing the values using median

```{r}
data_replaced_by_median <- data_prod
data_replaced_by_median$wip <- replace(data_replaced_by_median$wip,is.na(data_replaced_by_median$wip),median(data_replaced_by_median$wip,na.rm = TRUE))
head(data_replaced_by_median)
cat("The median of wip after removing all NA value rows is", median(data_replaced_by_median$wip,na.rm = TRUE))
```

The median is 1039, which is quite close to the mean.

5) Using Multivariate Imputation by Chained Equations (MICE): regress the missing variable as predictive from other variables.

```{r}
data_replaced_by_mice <- mice(data_prod,m=5,maxit=50,meth='pmm',seed=500)
#summary(data_replaced_by_mice)
```

```{r}
completeData <- complete(data_replaced_by_mice,2)
head(completeData)
```

In the codes above, we regress wip on other variables using predictive mean matching method. We generate 5 datasets and sex the maximum number of iteration to be 5. We select the second dataset as reference and display as the completeData above. 

The concern is that we have high portion of wip values depending on other variables (since we regresse wip on other variables.).


```{r}
# library(GGally)
# ggpairs(data_prod,columns = 9:15)
```

```{r}
ggplot(data_prod) + 
  geom_line(aes(x = day, y = actual_productivity,color=department, group=department)) + 
  #scale_y_continuous(limits = c(0.2, 1), breaks = seq(0, 1, by = 0.1))+
  labs(x="Day of the Week", y = "Actual Productivity", color = "Department") + 
  theme_minimal()
```





## References:

https://www.r-bloggers.com/2022/03/imputing-missing-values-in-r/
https://www.analyticsvidhya.com/blog/2016/03/tutorial-powerful-packages-imputing-missing-values/
https://cran.r-project.org/web/packages/mice/readme/README.html


## Create pie charts for categorical data to see the distributions:


```{r,warning = FALSE}
counts_of_departments = c(length(data_prod$department[data_prod$department=="sweing"]), length(data_prod$department[data_prod$department=="finishing"]))
labels_of_departments = c("sweing", "finishing")
departments_pie_labels <- paste0(labels_of_departments, ", ", round(100 * counts_of_departments/sum(counts_of_departments), 2), "%")

counts_of_quarters = c(length(data_prod$quarter[data_prod$quarter=="Quarter1"]), length(data_prod$quarter[data_prod$quarter=="Quarter2"]),length(data_prod$quarter[data_prod$quarter=="Quarter3"]), length(data_prod$quarter[data_prod$quarter=="Quarter4"]),length(data_prod$quarter[data_prod$quarter=="Quarter5"]))
labels_of_quarters = c("Quarter1", "Quarter2","Quarter3","Quarter4","Quarter5")
quarters_pie_labels <- paste0(labels_of_quarters, ", ", round(100 * counts_of_quarters/sum(counts_of_quarters), 2), "%")

counts_of_days = c(length(data_prod$day[data_prod$day=="Monday"]),
length(data_prod$day[data_prod$day=="Tuesday"]),
length(data_prod$day[data_prod$day=="Wednesday"]),
length(data_prod$day[data_prod$day=="Thursday"]),
length(data_prod$day[data_prod$day=="Friday"]),
length(data_prod$day[data_prod$day=="Saturday"]),
length(data_prod$day[data_prod$day=="Sunday"]))
labels_of_days = c("Monday","Tuesday","Wednesday","Thursday","Friday","Saturday","Sunday")
days_pie_labels <- paste0(labels_of_days, ", ", round(100 * counts_of_days/sum(counts_of_days), 2), "%")
```

```{r}
pie(counts_of_departments, labels = departments_pie_labels,main = "Pie Chart of Departments",col = rainbow(length(counts_of_departments)))
pie(counts_of_quarters, labels = quarters_pie_labels,main = "Pie Chart of Quarters",col = rainbow(length(counts_of_quarters)))
pie(counts_of_days, labels = days_pie_labels,main = "Pie Chart of Days",col = rainbow(length(counts_of_days)))
```



